### 2021-07-22 script/manuscript_clean_061021.Rmd
Update raw data and analyses scripts.

---
title: "manuscript_analysis_clean"
author: "Jojo Hu"
date: "06/10/2021"
output: html_document
---

# Manuscript Analysis Cleaned (02/18/2021)

``` {r}
# setwd("/manuscript")

allData <- read.csv("allSLData.csv")
```

# Section 1: Demographic Analyses

## Gender
```{r}
library(reshape)

allData_gender_wide <- allData[,c("part_id", "group", "gender")]

allData_gender_long <- melt(allData_gender_wide, id.vars = c("part_id", "group"))

gender_wide <- cast(allData_gender_long, group~value, length)

# Chi-square on gender
# p<0.05 tells us that they are not matched for gender between group
print(gender_wide)

print(chisq.test(gender_wide))
```

**Gender is matched between group**

## Age
```{r}
library(dplyr)

allData$age_at_web_year <- allData$age_at_web_month/12

allData %>%
  group_by(group) %>%
  dplyr::summarise(mean_age = mean(age_at_web_year), SD = sd(age_at_web_year), min = min(age_at_web_year), max = max(age_at_web_year)) %>%
  mutate_if(is.numeric, round, 2) %>%
  slice(match(c("TD", "ASD"), group))

allData_td <- 
  allData[which(allData$group == "TD"),]
allData_asd <- 
  allData[which(allData$group == "ASD"),]

#Test age difference between group, p <0.05 means age is significantly different between group
print(t.test(allData_td$age_at_web_year, allData_asd$age_at_web_year))
```

## Parental Report of Language Level in ASD
```{r}
allData %>%
  group_by(group, language_age_level) %>%
  dplyr::summarise(n = n())
```

## SCQ, RBS-R Descriptive Stat
```{r, include = F}
allData %>%
  dplyr::rename(scq_current = scq_total,
                scq_lifetime = scq_web) %>%
  group_by(group) %>%
  dplyr::summarise(across(c("scq_current", "scq_lifetime", "rbs_r"), 
                   list(mean = ~ mean(., na.rm = TRUE), SD = ~ sd(., na.rm = TRUE), N = ~ sum(!is.na(.))))) %>%
   slice(match(c("TD", "ASD"), group))
```

## SCQ T-tests
```{r}
# SCQ comparison between ASD and TD
t.test(allData_td$scq_total, allData_asd$scq_web)
```

## Remove outliers for RT and RT slope 
```{r}
library(stringr)

rt_hit_count_child <- read.csv("rt_hit_count_child.csv")
child_rt_outlier <- rt_hit_count_child[which(rt_hit_count_child$hit_trial_number < 6), ]
print(child_rt_outlier)
```
**Table above are RT outliers in children with less than 6 hit trials in the familiarization phase**

## Remove outliers in the children group
```{r, include = F}
outlier_extract <-
  function(DF, task) {
    part_id <- DF[which(DF$task == task), "part_id"]
    rt_col <- paste0(task, "_rt")
    slope_col <- paste0(task, "_slope")

    if(length(part_id) != 0) {
      allData[which(allData$part_id %in% part_id), 
              c(rt_col, slope_col)] <- NA
      }
    return(allData)
    }

allData <- outlier_extract(child_rt_outlier, "ssl")
allData <- outlier_extract(child_rt_outlier, "tsl")
allData <- outlier_extract(child_rt_outlier, "vsl")
allData <- outlier_extract(child_rt_outlier, "lsl")

print(child_rt_outlier)
```

**Above is removed outliers in the children group:**

**RT and Slope < 6 hits:+ 1 ASD spoli_c_097 (jsPsyc technical error in SSL RT)**

## Count the number of completed participants for each task
```{r,include = F}
allData$scq_web <- as.numeric(as.character(allData$scq_web))

completeCount <- function(group) {
  df <- sapply(allData[which(allData$group == group),
                       c("scq_web",
                         "scq_total",
                         "rbs_r",
                         "vsl_acc",
                         "lsl_acc",
                         "tsl_acc",
                         "ssl_acc")],
               function(x) sum(!is.na(x)))
  return(df)
}

taskcomp_td <- completeCount("TD")
taskcomp_asd <- completeCount("ASD")

taskcomp_count<- rbind(taskcomp_td, taskcomp_asd)
taskcomp_count <- data.frame(taskcomp_count)

colnames(taskcomp_count) <- c("SCQ Lifetime", "SCQ Current", "RBS-R", "Image", "Letter", "Tone", "Syllable")

missing_scq_web <- allData[which(is.na(allData$scq_web) & allData$group == "ASD"), "part_id"]

countThreeTask <- function(group) {
  threeTaskCount <- rowSums(!is.na(allData[which(allData$group == group),
                       c("vsl_acc", 
                           "lsl_acc",
                           "tsl_acc", 
                           "ssl_acc")]))
  return(threeTaskCount)
}
# Number of participants with 3 SL tasks
length(which(countThreeTask("TD") == 3))
length(which(countThreeTask("ASD") == 3))

print(taskcomp_count)
```

**Missing SCQ: spoli_c_439; spoli_c_448: No SCQ-L scores from SPARK; blast_c_438: Not from SPARK**

# Section 2: SL Group Comparison Reaction Time

## Preprocess by trial RT data, remove the RT Slope outliers
```{r, include = F}
rt_trial <- read.csv("rt_trial.csv")

outlier_extract_trial_rt <-
  function(DF, task) {
    part_id <- DF[which(DF$task == task), "part_id"]

    if (length(part_id) != 0) {
      rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }

rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "ssl")
rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "tsl")
rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "vsl")
rt_trial <- outlier_extract_trial_rt(child_rt_outlier, "lsl")

# Count N for each task
rt_trial %>%
  group_by(group, task) %>%
  summarize(n = length(unique(id))) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
```

## Number of hit trials in TD vs. ASD
```{r}
hit_trialN <- 
  rt_trial %>%
  subset(., !is.na(reaction_time)) %>%
  group_by(group, id, task) %>%
  dplyr::summarise(hit_trial_n = n())

# Count hits for each task
hit_trial_mean <-
  hit_trialN %>%
  group_by(group, task) %>%
  dplyr::summarise(
    mean_hit_trial = mean(hit_trial_n),
    sd = sd(hit_trial_n),
    n = n()
  ) %>%
  mutate(
    se = sd / sqrt(n),
    lower_ci = mean_hit_trial - qt(1 - (0.05 / 2), n - 1) * se,
    upper_ci = mean_hit_trial + qt(1 - (0.05 / 2), n - 1) * se
  ) %>%
  select(group, task, mean_hit_trial, lower_ci, upper_ci) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))

hit_trial_mean[,-c(1:2)] <- round(hit_trial_mean[,-c(1:2)], 2)

print(hit_trial_mean)
```

## Compare hit trials in TD vs. ASD
```{r}
library("stringr")
library("lmerTest")
add_dom_mod_func <-
  function(df) {
    df[which(str_detect(df$task, "ssl")), "domain"] <- "ling"
    df[which(str_detect(df$task, "lsl")), "domain"] <- "ling"
    df[which(str_detect(df$task, "vsl")), "domain"] <- "nonling"
    df[which(str_detect(df$task, "tsl")), "domain"] <- "nonling"
    df[which(str_detect(df$task, "ssl")), "modality"] <- "auditory"
    df[which(str_detect(df$task, "tsl")), "modality"] <- "auditory"
    df[which(str_detect(df$task, "vsl")), "modality"] <- "visual"
    df[which(str_detect(df$task, "lsl")), "modality"] <- "visual"
    return (df)
  }

hit_trialN <- add_dom_mod_func(hit_trialN)

m1_hit_trial <-
lmer(hit_trial_n ~ group*domain*modality + (1+domain+modality|id), data = hit_trialN,
       contrasts = list(group = c(-1,1),
                        domain = c(-1,1),
                        modality = c(-1,1)))

summary(m1_hit_trial)

hitsASD <- subset(hit_trialN, group == "ASD")
hitsTD <- subset(hit_trialN, group == "TD")

hit_trialN <- hit_trialN[!colnames(hit_trialN) %in% "group"]

# Add number of hits to the by trial RT data
rt_trial <- 
  merge(rt_trial, hit_trialN[,c("id", "task", "hit_trial_n")], by.x = c("id", "task"), by.y = c("id", "task"), all.x = T)

# Post-hoc t-tests for number of hits in each task
t.test(hitsTD[which(hitsTD$task == "lsl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "lsl"),]$hit_trial_n)
t.test(hitsTD[which(hitsTD$task == "ssl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "ssl"),]$hit_trial_n)
t.test(hitsTD[which(hitsTD$task == "vsl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "vsl"),]$hit_trial_n)
t.test(hitsTD[which(hitsTD$task == "tsl"),]$hit_trial_n, hitsASD[which(hitsASD$task == "tsl"),]$hit_trial_n)
```

## Normalize by trial raw RT for each participant and each task
```{r}
rt_trial_scaled <- rt_trial
rt_trial_scaled <- rt_trial_scaled[!is.na(rt_trial_scaled$reaction_time),]

for(id in unique(rt_trial_scaled$id)) {
    # Extract each id's individual rt by trial (normalized results below are the same as the scaled RT in the RT slope analyses; checked)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "lsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "vsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "tsl"),"reaction_time"], center = T)
    rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"), "scaled_rt"] <- 
      scale(rt_trial_scaled[which(rt_trial_scaled$id == id & rt_trial_scaled$task == "ssl"),"reaction_time"], center = T)

    # Using the first 3 target trials as baseline do not seem to be a very good idea; looking at the raw data the variances seem to be great among the first three trials:
    # firstThreeTrial <- sort(rt_trial_scaled[which(rt_trial_scaled$id == "blast_c_002" & rt_trial_scaled$task == "lsl"), "targ_index"])[1:3]
    # rt_trial_scaled[which(rt_trial_scaled$id == "blast_c_213" & rt_trial_scaled$targ_index %in% firstThreeTrial & rt_trial_scaled$task == "lsl"), ] 
}

# Add mean RT to by trial RT data
mean_rt <- allData[,c("part_id","lsl_rt", "vsl_rt", "tsl_rt", "ssl_rt")]
mean_rt <- melt(mean_rt, id.vars = ("part_id"))
colnames(mean_rt) <- c("part_id", "task", "mean_rt")
mean_rt$task <- gsub("_rt", "", mean_rt$task)
rt_trial_scaled <- merge(rt_trial_scaled, mean_rt, by.x = c("id", "task"), by.y = c("part_id", "task"), all.x = T)

hist(rt_trial_scaled$reaction_time)
hist(rt_trial_scaled$scaled_rt)
```

## SL Group Comparison RT: By Trial RT LMER
```{r}
rt_trial_scaled$reaction_time <- as.numeric(as.character(rt_trial_scaled$reaction_time))
rt_trial_scaled$id <- as.factor(rt_trial_scaled$id)
rt_trial_scaled$task <- as.factor(rt_trial_scaled$task)
rt_trial_scaled$targ_index <- as.numeric(as.character(rt_trial_scaled$targ_index))
rt_trial_scaled$mean_rt <- as.numeric(as.character(rt_trial_scaled$mean_rt))

rt_trial_scaled$group <- 
  factor(rt_trial_scaled$group,
         levels = c("ASD", 
                    "TD"))
rt_trial_scaled <- rt_trial_scaled[order(rt_trial_scaled$group), ]

rt_trial_scaled$domain <- 
  factor(rt_trial_scaled$domain,
         levels = c("nonling", 
                    "ling"))
rt_trial_scaled <- rt_trial_scaled[order(rt_trial_scaled$domain), ]

rt_trial_scaled$modality <- 
  factor(rt_trial_scaled$modality,
         levels = c("auditory", 
                    "visual"))
rt_trial_scaled <- rt_trial_scaled[order(rt_trial_scaled$modality), ]

head(rt_trial_scaled)
```

## RT Model that has isSingular Warning:
```{r}
# isSingular Warning:
lmer_slope_m1 <-
  lmer(
    scaled_rt ~ group*targ_index*domain*modality + (1+domain+modality|id),
    # + (0 + (modality + domain) | id),
    data = rt_trial_scaled,
    contrasts = list(
      group = c(-0.5, 0.5),
      modality = c(-0.5, 0.5),
      domain = c(-0.5, 0.5)
    ),
    control=lmerControl(optimizer = "bobyqa")
  )
summary(lmer_slope_m1)

rtTrialModel <- summary(lmer_slope_m1)
rtTrialModel$coefficients <- round(rtTrialModel$coefficients, 2)
write.csv(as.data.frame(rtTrialModel$coefficients), "rtTrialModel.csv")
# Troubleshoot the model (no success):
# library(afex)
# all_fit(lmerrt_scaled_m1)
# print(lmerrt_scaled_m1, correlation=TRUE)
```

## Trying Other RT Models:
```{r}
# Using raw reaction time and controlling for mean reaction time (isSingular Warning; Scaling issues)
lmer_slope_m2 <-
  lmer(reaction_time~group*targ_index*domain*modality + mean_rt + (1+domain+modality| id),
       data = rt_trial_scaled,
       contrasts = list(group = c(-0.5,0.5),
                        modality = c(-0.5, 0.5),
                        domain = c(-0.5, 0.5))
      )

summary(lmer_slope_m2)
```

## SL Group Comparison RT: Follow-up on four-way interaction (diagnostic group x trial order x domain x modality)
```{r}
rt_trial_scaledLING <- rt_trial_scaled[which(rt_trial_scaled$domain == "ling"),]
rt_trial_scaledNonling <- rt_trial_scaled[which(rt_trial_scaled$domain == "nonling"),]

lmer_slopeLING <-
  lmer(scaled_rt~group*targ_index*modality + (1+modality|id),
       data = rt_trial_scaledLING,
       contrasts = list(group = c(-1,1),
                        modality = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeLING)

rtTrialLingModel <- summary(lmer_slopeLING)
rtTrialLingModel$coefficients <- round(rtTrialLingModel$coefficients, 2)
write.csv(as.data.frame(rtTrialLingModel$coefficients), "rtTrialLingModel.csv")

lmer_slopeNonling <-
  lmer(scaled_rt~group*targ_index*modality + (1+modality|id),
       data = rt_trial_scaledNonling,
       contrasts = list(group = c(-1,1),
                        modality = c(-1, 1)),
       control=lmerControl(optimizer = "bobyqa"))

summary(lmer_slopeNonling)

rtTrialNonlingModel <- summary(lmer_slopeNonling)
rtTrialNonlingModel$coefficients <- round(rtTrialNonlingModel$coefficients, 2)
write.csv(as.data.frame(rtTrialNonlingModel$coefficients), "rtTrialNonlingModel.csv")
```

## SL Group Comparison RT Slope: Post-hoc T-tests TD vs. ASD
```{r}
t_test_multi_pair_slope <- 
  function(x,y){
  test <- t.test(x, y, alternative = "less")

  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

# RT slope
sapply(intersect(colnames(allData_td),colnames(allData_asd))[c(16:19)], 
                 function(x) t_test_multi_pair_slope(allData_td[,x], allData_asd[,x]))
```

# Section 3: SL Group Comparison Accuracy

## Preprocess SL data: Extract data for each measure (accuracy, slope, mean rt) and add domain and modality
```{r, include = F}
extract_measure_child <-
function(df, taskCol) {
  df <- 
    allData[,which(str_detect(
      colnames(allData), paste0("part_id|group|age_at_web_year|", taskCol)))]

  df <- melt(df, id.vars = c("part_id", "group", "age_at_web_year"))

  colnames(df)[colnames(df) == "variable"] <- "task"
  colnames(df)[colnames(df) == "value"] <- taskCol

  return(df)
}

allData_acc <- extract_measure_child(allData_acc, "acc")
allData_slope <- extract_measure_child(allData_slope, "slope")
allData_rt <- extract_measure_child(allData_rt, "rt")

colnames(allData_acc)[colnames(allData_acc) == "acc"] <- "accuracy"
colnames(allData_rt)[colnames(allData_rt) == "rt"] <- "mean_rt"
colnames(allData_slope)[colnames(allData_slope) == "slope"] <- "rt_slope"

# Add modality and domain category to long-format data
allData_acc <- add_dom_mod_func(allData_acc)
allData_rt <- add_dom_mod_func(allData_rt)
allData_slope <- add_dom_mod_func(allData_slope)
```

## SL against chance for TD and ASD
```{r}
t_test_against_chance <- 
  function(x){
  test <- t.test(x, mu=0.5, alternative= "greater")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

#TD
sapply(colnames(allData_td)[c(7:10)], 
       function(x) t_test_against_chance(allData_td[,x]))

#ASD
sapply(colnames(allData_asd)[c(7:10)], 
       function(x) t_test_against_chance(allData_asd[,x]))

t_test_against_zero <- 
  function(x){
  test <- t.test(x, mu=0, alternative= "less")
  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

#TD
sapply(colnames(allData_td)[c(16:19)], 
       function(x) t_test_against_zero(allData_td[,x]))

#ASD
sapply(colnames(allData_asd)[c(16:19)], 
       function(x) t_test_against_zero(allData_asd[,x]))
```

## SL Group Comparison Accuracy: By Trial Accuracy GLMER
```{r}
acc_trial <- read.csv("acc_trial.csv")

acc_trial$task <- as.factor(acc_trial$task)
acc_trial$subj <- as.factor(acc_trial$subj)
acc_trial$age_at_web_year <- as.numeric(as.character(acc_trial$age_at_web_year))

acc_trial$group <- 
  factor(acc_trial$group,
         levels = c("ASD", 
                    "TD"))
acc_trial <- acc_trial[order(acc_trial$group),]

acc_trial$domain <- 
  factor(acc_trial$domain,
         levels = c("nonling", 
                    "ling"))
acc_trial <- acc_trial[order(acc_trial$domain),]

acc_trial$modality <- 
  factor(acc_trial$modality,
         levels = c("auditory", 
                    "visual"))
acc_trial <- acc_trial[order(acc_trial$modality),]

head(acc_trial)
```

```{r}
logacc_dom <-
  glmer(corr~group*domain*modality + (1+domain+modality|subj), data = acc_trial,
    family = binomial,
    contrasts = list(domain = c(-0.5, 0.5), modality = c(-0.5, 0.5), group = c(-0.5,0.5)),
    control=glmerControl(optimizer = "bobyqa"))

summary(logacc_dom)

accModel <- summary(logacc_dom)
accModel <- round(accModel$coefficients, 2)
write.csv(as.data.frame(accModel), "accModel.csv")
```

## SL Group Comparison Accuracy: Post-hoc T-test TD vs. ASD
```{r}
t_test_multi_pair <- 
  function(x,y){
  test <- t.test(x, y, alternative = "greater")

  data.frame(p_value = test$p.value,
             df = test$parameter,
             t_stat = test$statistic)
  }

# Accuracy
sapply(intersect(colnames(allData_td),colnames(allData_asd))[c(7:10)], 
                 function(x) t_test_multi_pair(allData_td[,x], allData_asd[,x]))
```

# Section 4: SL Group Comparison Composite Scores

## Preprocess and calculate composite scores
```{r}
compositeAge <- allData
# Scale RT slopes across participants for each task
compositeAge[, c("lsl_slopeScaled", "ssl_slopeScaled","vsl_slopeScaled", "tsl_slopeScaled")] <-
  lapply(compositeAge[, c("lsl_slope", "ssl_slope","vsl_slope", "tsl_slope")], 
         function(x) {
           scale(0 - x, center = T)
           })
# Scale percentage correct across participants for each task
compositeAge[, c("lsl_accScaled", "ssl_accScaled","vsl_accScaled", "tsl_accScaled")] <-
  lapply(compositeAge[, c("lsl_acc", "ssl_acc","vsl_acc", "tsl_acc")], 
         function(x) {
           scale(x, center = T)
           })
# Calculate composite scores
sumComposite <- function(taskCol, nCol, column_list) {
  # Step 1: Sum the relevant scaled RT slopes and scaled percentage correct columns
  compositeAge[, taskCol] <-
    rowSums(compositeAge[, column_list], na.rm = T)
  # Step 2: Count the number of non-NA values out of the relevant scaled RT slopes and scaled percentage correct columns
  compositeAge[, nCol] <-
    apply(compositeAge[column_list], 1, function(x) {
      sum(!is.na(x))
    })
  # Calcualte the mean composite scores (Step 1 / Step 2)
  compositeAge[, taskCol] <-
    compositeAge[, taskCol] / compositeAge[, nCol]

  return(compositeAge)
}
# Linguistic SL composite score
compositeAge <-
  sumComposite("composite_ling", "completeN_ling", 
               c("lsl_accScaled", "ssl_accScaled", 
                 "lsl_slopeScaled", "ssl_slopeScaled"))
# Nonlinguistic SL composite score
compositeAge <-
  sumComposite("composite_nonling", "completeN_nonling", 
               c("vsl_accScaled", "tsl_accScaled", 
                 "vsl_slopeScaled", "tsl_slopeScaled"))
# Letter SL composite score
compositeAge <-
  sumComposite("composite_lsl", "completeN_lsl", 
               c("lsl_accScaled", "lsl_slopeScaled"))
# Syllable SL composite score
compositeAge <-
  sumComposite("composite_ssl", "completeN_ssl", 
               c("ssl_accScaled", "ssl_slopeScaled"))
# Image SL composite score
compositeAge <-
  sumComposite("composite_vsl", "completeN_vsl", 
               c("vsl_accScaled", "vsl_slopeScaled"))
# Tone SL composite score
compositeAge <-
  sumComposite("composite_tsl", "completeN_tsl", 
               c("tsl_accScaled", "tsl_slopeScaled"))

```

## Descriptive stats of accuracy and RT slopes (in all participants, or Younger and Older age groups)
```{r}
compositeAge <- compositeAge

getDescripStat <- function(group, col) {
  compositeAge %>%
      group_by(!!as.symbol(group)) %>%
      dplyr::summarise(mean = mean((!!as.symbol(col)), na.rm = TRUE),
                sd = sd((!!as.symbol(col)), na.rm = TRUE),
                n = n()) %>%
      mutate(se = sd / sqrt(n),
             lower_ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
             upper_ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
      select(!!as.symbol(group), mean, lower_ci, upper_ci) %>%
    slice(match(c("TD", "ASD"), group))
}

getDescripStat("group", "lsl_acc")
getDescripStat("group", "ssl_acc")
getDescripStat("group", "vsl_acc")
getDescripStat("group", "tsl_acc")

getDescripStat("group", "lsl_slope")
getDescripStat("group", "ssl_slope")
getDescripStat("group", "vsl_slope")
getDescripStat("group", "tsl_slope")

getDescripStat("group", "composite_lsl")
getDescripStat("group", "composite_ssl")
getDescripStat("group", "composite_vsl")
getDescripStat("group", "composite_tsl")

# getDescripStat("age_group", "composite_ling")
# getDescripStat("age_group", "composite_nonling")
```

## SL Group Comparison Composite: SL Composite Scores LMER
```{r}
compositeGroup <-
  compositeAge[, c(
    "part_id",
    "group",
    "gender",
    "age_at_web_month",
    "age_at_web_year",
    "composite_lsl",
    "composite_ssl",
    "composite_vsl",
    "composite_tsl")]

compositeGroupL <-
  melt(
    compositeGroup,
    id.vars = c(
      "part_id",
      "group",
      "gender",
      "age_at_web_month",
      "age_at_web_year"))

colnames(compositeGroupL)[colnames(compositeGroupL) %in% c("variable", "value")] <- c("task", "composite_score")
compositeGroupL <- add_dom_mod_func(compositeGroupL)
compositeGroupL$task <- as.factor(compositeGroupL$task)
compositeGroupL$part_id <- as.factor(compositeGroupL$part_id)
compositeGroupL$age_at_web_month <- as.numeric(as.character(compositeGroupL$age_at_web_month))
compositeGroupL$composite_score <- as.numeric(as.character(compositeGroupL$composite_score))

compositeGroupL$group <-
  factor(compositeGroupL$group,
         levels = c("ASD",
                    "TD"))
compositeGroupL <- compositeGroupL[order(compositeGroupL$group),]

compositeGroupL$domain <-
  factor(compositeGroupL$domain,
         levels = c("nonling",
                    "ling"))
compositeGroupL <- compositeGroupL[order(compositeGroupL$domain),]

compositeGroupL$modality <-
  factor(compositeGroupL$modality,
         levels = c("auditory",
                    "visual"))
compositeGroupL <- compositeGroupL[order(compositeGroupL$modality),]

head(compositeGroupL)
```

```{r}
composite_m1 <-
  lmer(composite_score ~ group*domain*modality + (1+domain+modality|part_id),
       data = compositeGroupL,
       contrasts = list(domain = c(-0.5, 0.5), modality = c(-0.5, 0.5), group = c(-0.5, 0.5)))
summary(composite_m1)

compositeModel <- summary(composite_m1)
compositeModel <- round(compositeModel$coefficients, 2)
write.csv(as.data.frame(compositeModel), "compositeModel.csv")
```

## SL Group Comparison Composite: Post-hoc T-test TD vs. ASD
```{r}
compositeGroupTD <- compositeGroup[which(compositeGroup$group == "TD"),]
compositeGroupASD <- compositeGroup[which(compositeGroup$group == "ASD"),]

# one-tailed t-test TD > ASD
sapply(intersect(colnames(compositeGroupTD),colnames(compositeGroupASD))[6:9], 
                 function(x) t_test_multi_pair(compositeGroupTD[,x], compositeGroupASD[,x]))
```

# Section 5: SL Cross-sectional Development Analyses

## Preprocess: scale age and re-scale SL composite scores
```{r}
# IMPORTANT: Scale age so that age is on the same scale as composite scores
compositeAge$age_scaled <- scale(compositeAge$age_at_web_year, center = T)
# Regenerate a long data frame with GJT and composite scores across domains
compositeAgeL <-
  melt(
    compositeAge[, c(
      "part_id",
      "group",
      "age_at_web_month",
      "age_at_web_year",
      "age_scaled",
      "a_prime",
      "scq_web",
      "rbs_r",
      "composite_nonling",
      "composite_ling"
    )],
    id.vars = c(
      "part_id",
      "group",
      "age_at_web_month",
      "age_at_web_year",
      "age_scaled",
      "a_prime",
      "scq_web",
      "rbs_r"
    )
  )

colnames(compositeAgeL)[which(colnames(compositeAgeL) == "variable")] <- "domain"
colnames(compositeAgeL)[which(colnames(compositeAgeL) == "value")] <- "composite_score"
```

## SL Cross-sectional Development Analyses: Continous Age and Composite Scores LMER
```{r}
compositeAgeL$domain <- as.factor(compositeAgeL$domain)
compositeAgeL$group <- as.factor(compositeAgeL$group)
compositeAgeL$age_scaled <- as.numeric(as.character((compositeAgeL$age_scaled)))

nCount <-
compositeAgeL %>%
  group_by(part_id) %>%
  dplyr::summarise(n = n())

which(nCount$n == 1)
# Every participant has a linguistic and a nonlinguistic composite score

compositeAgeL$domain <-
  factor(compositeAgeL$domain,
         levels = c("composite_nonling", "composite_ling"))
compositeAgeL <- compositeAgeL[order(compositeAgeL$domain), ]

compositeAgeL$group <-
  factor(compositeAgeL$group, levels = c("ASD", "TD"))
compositeAgeL <- compositeAgeL[order(compositeAgeL$group), ]

# Save non-scaled composite scores for other analyses
compositeAgeLNscaled <- compositeAgeL
hist(compositeAgeLNscaled$composite_score)

# Rescaling the composite score so that age and compsite scores are on the same scale; no scaling of composite scores yields similar model results with different estimates
compositeAgeL$composite_score <- scale(compositeAgeL$composite_score)
hist(compositeAgeL$composite_score)

age_composite_m1 <- 
  lmer(composite_score ~ group*domain*age_scaled + (1|part_id),  
       data = compositeAgeL,
      contrasts = list(domain = c(-0.5, 0.5),
                       group = c(-0.5, 0.5))
     )
summary(age_composite_m1)

ageCompositeModel <- summary(age_composite_m1)
ageCompositeModel <- round(ageCompositeModel$coefficients, 2)
write.csv(ageCompositeModel, "ageCompositeModel.csv")
```

## Assign age groups
```{r}
compositeAge <- compositeAge[order(compositeAge$age_at_web_month),]
# hist(compositeAge$age_at_web_year)

# Median split of age across all the participants
compositeAge[1:round(length(compositeAge$age_at_web_month)/2),"age_group"] <- "Younger"
compositeAge[which(compositeAge$group == "TD" & compositeAge$age_group == "Younger"), "age_group"] <- "Younger TD"
compositeAge[which(compositeAge$group == "ASD" & compositeAge$age_group == "Younger"), "age_group"] <- "Younger ASD"

median <- round((length(compositeAge$age_at_web_month)/2))+1
compositeAge[median:length(compositeAge$age_at_web_month),"age_group"] <- "Older"
compositeAge[which(compositeAge$group == "TD" & compositeAge$age_group == "Older"), "age_group"] <- "Older TD"
compositeAge[which(compositeAge$group == "ASD" & compositeAge$age_group == "Older"), "age_group"] <- "Older ASD"

compositeAge$ageSplit <- str_extract(compositeAge$age_group, "Young|Old")

# Mean split of age in each diagnostic group

# compositeAgeTD[which(compositeAgeTD$age_at_web_month < mean(compositeAgeTD$age_at_web_month)),"age_group"] <- "Younger TD"
# compositeAgeTD[which(compositeAgeTD$age_at_web_month > mean(compositeAgeTD$age_at_web_month)),"age_group"] <- "Older TD"
# compositeAgeASD[which(compositeAgeASD$age_at_web_month < mean(compositeAgeASD$age_at_web_month)),"age_group"] <- "Younger ASD"
# compositeAgeASD[which(compositeAgeASD$age_at_web_month > mean(compositeAgeASD$age_at_web_month)),"age_group"] <- "Older ASD"

# Check children younger than 6.5's accuracy (compared to Arnon's results)
# compositeAge[which(compositeAge$age_at_web_year < 6.5 & compositeAge$group == "TD"), "ssl_acc"]
```

## Age stats in Younger and Older age groups
```{r}
library(reshape2)
age_wide <- dcast(compositeAge, group~ageSplit, length)
print(age_wide)
# print(chisq.test(age_wide))

compositeAge %>%
    group_by(ageSplit) %>%
    dplyr::summarise(mean_age_month = mean(age_at_web_month), mean_age_year = round(mean(age_at_web_year),2), sd = sd(age_at_web_year), n = n())

oldYoungAge <- 
  compositeAge %>%
    group_by(group, ageSplit) %>%
    dplyr::summarise(mean_age_month = mean(age_at_web_month), mean_age_year = mean(age_at_web_year), sd = sd(age_at_web_year), n = n())

oldYoungAge[, -c(1:2)] <- round(oldYoungAge[, -c(1:2)], 2)

print(oldYoungAge)

compositeAgeTD <- compositeAge[which(compositeAge$group == "TD"),]
compositeAgeASD <- compositeAge[which(compositeAge$group == "ASD"),]

compositeAgeTDY <- compositeAgeTD[which(compositeAgeTD$ageSplit == "Young"),]
compositeAgeTDO <- compositeAgeTD[which(compositeAgeTD$ageSplit == "Old"),]

compositeAgeASDY <- compositeAgeASD[which(compositeAgeASD$ageSplit == "Young"),]
compositeAgeASDO <- compositeAgeASD[which(compositeAgeASD$ageSplit == "Old"),]

t.test(compositeAgeTDY$age_at_web_year, compositeAgeASDY$age_at_web_year)
t.test(compositeAgeTDO$age_at_web_year, compositeAgeASDO$age_at_web_year)
```

## SL Cross-sectional Development Analyses: Follow-up in Younger and Older age groups
```{r}
compositeAgeLNscaled <- merge(compositeAgeLNscaled, compositeAge[,c("part_id", "age_group", "ageSplit")], by.x = "part_id", by.y = "part_id", all.x = T)
compositeYoungL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Young"),]
compositeOldL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Old"),]

compositeAgeLNscaled$ageSplit <- as.factor(compositeAgeLNscaled$ageSplit)

compositeAgeLNscaled$ageSplit <-
  factor(compositeAgeLNscaled$ageSplit, levels = c("Young", "Old"))
compositeAgeLNscaled <- compositeAgeLNscaled[order(compositeAgeLNscaled$ageSplit),]

compositeAgeLNscaled$domain <-
  factor(compositeAgeLNscaled$domain,
         levels = c("composite_nonling", "composite_ling"))
compositeAgeLNscaled <- compositeAgeLNscaled[order(compositeAgeLNscaled$domain),]

compositeAgeLNscaled$group <-
  factor(compositeAgeLNscaled$group,
         levels = c("ASD", "TD"))
compositeAgeLNscaled <- compositeAgeLNscaled[order(compositeAgeLNscaled$group),]

head(compositeAgeLNscaled)
```
## SL Cross-sectional Development Analyses: Younger group model has isSingular Warnings
```{r}
# Rescaling in each age group:
compositeOldL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Old"),]
compositeOldL$composite_score <- scale(compositeOldL$composite_score)

# Rescaling in each age group:
compositeYoungL <- compositeAgeLNscaled[which(compositeAgeLNscaled$ageSplit == "Young"),]
compositeYoungL$composite_score <- scale(compositeYoungL$composite_score)

# Younger group has isSingular Warnings
age_composite_m3 <- 
  lmer(composite_score ~ group*domain + (1|part_id),  
       data = compositeYoungL,
     contrasts = list(domain = c(-0.5, 0.5),
                      group = c(-0.5, 0.5))
     )

summary(age_composite_m3)

# all_fit(age_composite_m3)

ageCompositeYoungModel <- summary(age_composite_m3)
ageCompositeYoungModel <- round(ageCompositeYoungModel$coefficients, 2)
write.csv(ageCompositeYoungModel, "ageCompositeYoungModel.csv")

age_composite_m2 <- 
  lmer(composite_score ~ group*domain + (1|part_id),  
       data = compositeOldL,
     contrasts = list(domain = c(-0.5, 0.5),
                  group = c(-0.5, 0.5))
     )

summary(age_composite_m2)

ageCompositeOldModel <- summary(age_composite_m2)
ageCompositeOldModel <- round(ageCompositeOldModel$coefficients, 2)
write.csv(ageCompositeOldModel, "ageCompositeOldModel.csv")
```

## SL Cross-sectional Development Analyses: Post-hoc t-test of Linguistic SL Composite Scores in each age group
```{r}
# Younger group:
t.test(compositeAgeTDY$composite_ling, compositeAgeASDY$composite_ling, alternative = "greater")
# Older group:
t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling, alternative = "greater")
```

# Section 6: Task Correlation analyses

## Preprocess: re-scale SL composite scores in each task
```{r}
mulregScaled <- compositeAge[,c("part_id", "group", "age_at_web_month", "age_at_web_year", "age_scaled", "a_prime",
                               "scq_web", "rbs_r", "composite_ling", "composite_nonling", "ageSplit",
                              "composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")]

# Scale the data 
mulregScaled[, c("composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")] <-
  lapply(mulregScaled[, c("composite_lsl", "composite_ssl","composite_tsl", "composite_vsl")], 
         function(x) {
           scale(x, center = T)
           })
```

## Planned Letter and Syllable SL analyses: Compare composite LSL and composite SSL relationship based on Age
```{r}
mulregScaled$ageSplit <- 
  factor(mulregScaled$ageSplit,levels = c("Young", "Old"))
mulregScaled <- mulregScaled[order(mulregScaled$ageSplit),]

mulregScaled$group <- 
  factor(mulregScaled$group,levels = c("ASD", "TD"))
mulregScaled <- mulregScaled[order(mulregScaled$group),]

head(mulregScaled)
```

```{r}
compositeCorr_m1 <- lm(composite_lsl ~ group*ageSplit*composite_ssl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5),
                      ageSplit = c(-0.5, 0.5)))

summary(compositeCorr_m1)

compositeCorrModel <- summary(compositeCorr_m1)
compositeCorrModel <- compositeCorrModel$coefficients
compositeCorrModel <- round(compositeCorrModel, 2)
write.csv(compositeCorrModel, "compositeCorrModel.csv")

# When age was fit as a continous variable:
compositeCorr_m2 <- lm(composite_lsl ~ group*age_scaled*composite_ssl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5)
                      ))

summary(compositeCorr_m2)
```

## Follow-up on Letter and Syllable Letter and Syllable SL analyses: composite LSL and composite SSL relationship in each age group
```{r}
mulregScaledY <- mulregScaled[which(mulregScaled$ageSplit == "Young"),]
mulregScaledO <- mulregScaled[which(mulregScaled$ageSplit == "Old"),]

# Fitting the not re-scaled composite SL scores also did not change the results:
compositeCorr_m3 <- lm(composite_lsl ~ group*composite_ssl, data = mulregScaledY,
                      contrasts = list( 
                      group = c(-0.5, 0.5)))

summary(compositeCorr_m3)

compositeCorrYoungModel <- summary(compositeCorr_m3)
compositeCorrYoungModel <- compositeCorrYoungModel$coefficients
compositeCorrYoungModel <- round(compositeCorrYoungModel, 2)
write.csv(compositeCorrYoungModel, "compositeCorrYoungModel.csv")

compositeCorr_m4 <- lm(composite_lsl ~ group*composite_ssl, data = mulregScaledO,
                      contrasts = list( 
                      group = c(-0.5, 0.5)))

summary(compositeCorr_m4)

compositeCorrOldModel <- summary(compositeCorr_m4)
compositeCorrOldModel <- compositeCorrOldModel$coefficients
compositeCorrOldModel <- round(compositeCorrOldModel, 2)
write.csv(compositeCorrOldModel, "compositeOldCorrModel.csv")
```

## Follow-up on Letter and Syllable SL analyses: Extract Pearson's R between composite LSL and composite SSL in each age group 
```{r} 
getCorrCI <- 
  function(df, group, age, col1, col2) {
      corTestDF <- cor.test(df[,c(col1)], df[,c(col2)])
      pearsonr <- corTestDF$estimate
      ci_upper <- corTestDF$conf.int[1]
      ci_lower <- corTestDF$conf.int[2]
      p_value <- corTestDF$p.value
      n <- corTestDF$parameter + 2

      tempDF <- data.frame(cbind(pearsonr, ci_upper, ci_lower, p_value, n))

      tempDF$Group <- group
      tempDF$Age <- age

      return(tempDF)
  }

lingCorrTDY <- getCorrCI(compositeAgeTDY, "TD", "Young", "composite_lsl", "composite_ssl")
lingCorrTDO <- getCorrCI(compositeAgeTDO, "TD", "Old", "composite_lsl", "composite_ssl")
lingCorrASDY <- getCorrCI(compositeAgeASDY, "ASD", "Young", "composite_lsl", "composite_ssl")
lingCorrASDO <- getCorrCI(compositeAgeASDO, "ASD", "Old", "composite_lsl", "composite_ssl")

lingCorr <- rbind(lingCorrTDY, lingCorrTDO, lingCorrASDY, lingCorrASDO)
# two-tailed p values
print(lingCorr)
```

## Follow-up on Letter and Syllable SL analyses: Simple correlation comparison on composite LSL and SSL relationship in TD vs. ASD
```{r}
library(cocor)

# Compare Linguistic SL composite scores between young TD and young ASD
cocor.indep.groups(r1.jk=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Young"), "pearsonr"], 
                   r2.hm=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Young"), "pearsonr"], 
                   n1=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Young"), "n"], 
                   n2=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Young"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
# Compare Linguistic SL composite scores between old TD and old ASD
cocor.indep.groups(r1.jk=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Old"), "pearsonr"], 
                   r2.hm=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Old"), "pearsonr"], 
                   n1=lingCorr[which(lingCorr$Group == "TD" & lingCorr$Age == "Old"), "n"], 
                   n2=lingCorr[which(lingCorr$Group == "ASD" & lingCorr$Age == "Old"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```

## Planned Letter and Image SL analyses: Compare composite LSL and composite VSL relationship based on Age
```{r}
compositeCorr_m3 <- lm(composite_lsl ~ group*ageSplit*composite_vsl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5),
                      ageSplit = c(-0.5, 0.5)))

summary(compositeCorr_m3)

# When age was fit as a continous variable:
compositeCorr_m4 <- lm(composite_lsl ~ group*age_scaled*composite_vsl, data = mulregScaled,
                      contrasts = list( 
                      group = c(-0.5, 0.5)
                      ))

summary(compositeCorr_m4)
```

## Planned Analyses: Extract task correlations across all age
```{r}
getCorrComposite <-
function(df, group, age, task, col1, col2) {
      corTestDF <- cor.test(df[,c(col1)], df[,c(col2)])
      pearsonr <- corTestDF$estimate
      ci_upper <- corTestDF$conf.int[1]
      ci_lower <- corTestDF$conf.int[2]
      p_value <- corTestDF$p.value
      n <- corTestDF$parameter + 2

      tempDF <- data.frame(cbind(pearsonr, ci_upper, ci_lower, p_value, n))

      tempDF$Group <- group
      tempDF$Age <- age
      tempDF$Task <- task

      return(tempDF)
  }

lingCorrTDlsl_ssl <- getCorrComposite(compositeAgeTD, "TD", "all_age", "lsl_ssl", "composite_lsl", "composite_ssl")
lingCorrASDlsl_ssl <- getCorrComposite(compositeAgeASD, "ASD", "all_age", "lsl_ssl", "composite_lsl", "composite_ssl")
lingCorrTDlsl_vsl <- getCorrComposite(compositeAgeTD, "TD", "all_age", "lsl_vsl", "composite_lsl", "composite_vsl")
lingCorrASDlsl_vsl <- getCorrComposite(compositeAgeASD, "ASD", "all_age", "lsl_vsl", "composite_lsl", "composite_vsl")

lingCorrLSL <- rbind(lingCorrTDlsl_ssl, lingCorrASDlsl_ssl, lingCorrTDlsl_vsl, lingCorrASDlsl_vsl)

print(lingCorrLSL)

cor.test(compositeAgeTD$composite_lsl, compositeAgeTD$composite_vsl)
cor.test(compositeAgeTD$composite_lsl, compositeAgeTD$composite_ssl)
```

## Follow-up on Letter and Syllable SL analyses: Simple correlation comparison on composite LSL and SSL relationship in TD vs. ASD
```{r}
# Compare composite LSL/ SSL correlations between TD and ASD
cocor.indep.groups(r1.jk=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_ssl"), "pearsonr"], 
                   r2.hm=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_ssl"), "pearsonr"], 
                   n1=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_ssl"), "n"], 
                   n2=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_ssl"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```

## Follow-up on Letter and Image SL analyses: Simple correlation comparison on composite LSL and VSL relationship in TD vs. ASD
```{r}
# Compare composite LSL/ SSL correlations between TD and ASD
cocor.indep.groups(r1.jk=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_vsl"), "pearsonr"], 
                   r2.hm=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_vsl"), "pearsonr"], 
                   n1=lingCorrLSL[which(lingCorrLSL$Group == "TD" & lingCorrLSL$Task == "lsl_vsl"), "n"], 
                   n2=lingCorrLSL[which(lingCorrLSL$Group == "ASD" & lingCorrLSL$Task == "lsl_vsl"), "n"], 
                   alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```

# Section 8: Prep Plotting

## Letter and Syllable SL analyses: Plot Letter and Syllable SL Composite Scores Correlation in each age group
```{r}
library("dplyr")
library("TeachingDemos")
library("ggpattern")
library("ggplot2")

cbPalette <- c('#a6cee3','#1f78b4','#b2df8a', '#66c2a5','#fc8d62','#8da0cb', '#1b9e77','#d95f02','#7570b3')
cbPaletteGrey <- col2grey(cbPalette)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("Young", "Old")

lingCorr %>%
  ggplot(aes(
    x = Group,
    y = pearsonr,
    ymin = ci_lower,
    ymax = ci_upper,
    fill = Group
  )) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.9) +
  facet_wrap("Age", labeller = (labeller(Age = labs))) +
  geom_col_pattern(color = "black",
                   pattern = "null") +
  scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
  geom_errorbar(width = .1, position = position_dodge(width = 0.9)) +
  labs(title = "Relationship between Letter and Syllable SL Composite Scores",
       x = "Group",  # Change x-axis label
       y = "Pearson's Correlation Estimate") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 29, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.position = c(0.064, 0.88),
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  geom_text(
    size = 14,
    color = "black",
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.85, label = paste0("*"))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.85,
      yend = 0.85
    ),
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    )
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.85,
      yend = 0.85
    ),
    data = data.frame(
      Group = "TD",
      pearsonr = 0.55,
      Age = "Old",
      ci_upper = 0,
      ci_lower = 0,
      Domain = 0
    )
  )

# ggsave("composite_lsl_ssl.png",
#         bg="transparent", width = 26, height = 15, units = "cm")
```

## Accuracy Line Plot (no outliers)
## Preprocess: set up within subject standard error function
```{r}
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  merge(datac, ndatac)
}

summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

## Preprocess: calculate within subject standard error for accuracy
```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(data.table)
library("pastecs")

bar_all <-  allData[,c(which(str_detect(colnames(allData), 
                                          "part_id|group|ssl|lsl|vsl|tsl")))]
stat_desc <- 
function(df,group,task) {
  stat.desc(df[which(df$group == group & df$variable == task),])
}

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))

bar_acc <-
  bar_all_long[which(str_detect(
    bar_all_long$variable, "\\S{1}(?=sl_acc)")),]

library("data.table")

bar_acc$variable <-
revalue(bar_acc$variable, c("lsl_acc"="Letter",
                                     "vsl_acc"="Image",
                                   "tsl_acc"="Tone",
                                     "ssl_acc"="Syllable"))

bar_acc$variable <- 
  factor(bar_acc$variable,levels = c("Image", 
                                              "Letter", 
                                              "Tone", 
                                              "Syllable"))
bar_acc <-
  bar_acc[order(bar_acc$variable), ]

bar_acc$value <- 
  as.numeric(as.character(bar_acc$value))

detach(package:plyr)

acc_within_stat <- summarySEwithin(bar_acc, measurevar="value", betweenvars = "group",
                                   withinvars="variable", idvar="part_id", na.rm=T, conf.interval=.95)

colnames(acc_within_stat)[colnames(acc_within_stat) == "group"] <- "Group"

acc_within_stat$variable <-
  factor(acc_within_stat$variable,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))
```

## Plot Accuracy Line Plot
```{r}
pd <- position_dodge(width = 0.2)

acc_within_stat %>%
  ggplot(aes(x = variable, y = value, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(aes(ymin = value - se, ymax = value + se),
                width = .1,
                position = pd) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "2AFC Accuracy",
       x = "SL Task",  # Change x-axis label
       y = "Mean Accuracy (%)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 26, face = "bold"),
    axis.title.x = element_text(size = 21, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  ) +
  geom_hline(yintercept = 0.5, color = "grey") +
  geom_text(aes(
    x = 1.1,
    y = 0.505,
    label = paste0("chance", "-level")
  ), size = 5) +
  geom_text(aes(
    x = 0.95,
    y = 0.7,
    label = paste0("***")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(x = 1.95, y = 0.7, label = paste0("**")),
            size = 10,
            color = cbPalette[1]) +
  geom_text(aes(
    x = 2.95,
    y = 0.7,
    label = paste0("***")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(x = 3.95, y = 0.7, label = paste0("**")),
            size = 10,
            color = cbPalette[1]) +
  # geom_text(aes(x= 4.05, y = 0.7, label = paste0("†")), size=7, color="#00BFC4") +
  geom_text(aes(x = 3.05, y = 0.51, label = paste0("*")),
            size = 10,
            color = cbPalette[8]) +
  # geom_text(aes(x= 1.95, y = 0.51, label = paste0("†")), size=7, color="#F8766d") +
  geom_text(aes(x = 4.05, y = 0.51, label = paste0("**")),
            size = 10,
            color = cbPalette[8]) +
  geom_text(aes(x = 2.05, y = 0.494, label = paste0("*")),
            size = 10,
            color = cbPalette[8])

# ggsave("behavioral_acc_across_group.png",
#        bg="transparent",width = 15, height = 15, units = "cm")
```

## Preprocess: calculate within subject standard error for RT slope
```{r}
library(dplyr)
library(ggplot2)

bar_all_long <- melt(bar_all, id.vars=c("part_id", "group"))

bar_slope <-
  bar_all_long[which(
    str_detect(bar_all_long$variable, "\\S{3}(?=_slope)")),]

bar_slope$variable <-
revalue(bar_slope$variable, c("lsl_slope"="Letter",
                                     "vsl_slope"="Image",
                                     "tsl_slope"="Tone",
                                     "ssl_slope"="Syllable"))

bar_slope$variable <- 
  factor(bar_slope$variable,levels = c("Image", 
                                                  "Letter", 
                                                  "Tone", 
                                                  "Syllable"))

bar_slope <-
  bar_slope[order(bar_slope$variable), ]

bar_slope$value <- 
  as.numeric(as.character(bar_slope$value))

detach(package:plyr)
slope_within_stat <- summarySEwithin(bar_slope, measurevar="value", betweenvars = "group", withinvars="variable",
                        idvar="part_id", na.rm=T, conf.interval=.95)

colnames(slope_within_stat)[colnames(slope_within_stat) == "group"] <- "Group"
colnames(slope_within_stat)[colnames(slope_within_stat) == "value"] <- "mean"
colnames(slope_within_stat)[colnames(slope_within_stat) == "se"] <- "std_error"
colnames(slope_within_stat)[colnames(slope_within_stat) == "variable"] <- "task"

slope_within_stat$task <-
  factor(slope_within_stat$task,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))

slope_within_stat$Group <-
  factor(slope_within_stat$Group, levels = c("TD",
                                             "ASD"))
```

## Plot RT Slope Line Plot (outliers removed)
```{r}
pd <- position_dodge(width = 0.2)

slope_within_stat %>%
  ggplot(aes(x = task, y = mean, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(
    aes(ymin = mean - std_error, ymax = mean + std_error),
    width = .1,
    position = pd
  ) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "SL Reaction Time Slope",
       x = "SL Task",  # Change x-axis label
       y = "Mean Reaction Time Slope (arbitrary unit/trial)") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  # scale_y_reverse() +
  theme(plot.title = element_text(hjust = 0.35)) +
  theme(
    plot.title = element_text(size = 26, face = "bold"),
    axis.title.x = element_text(size = 21, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )  +
  geom_hline(yintercept = 0, color = "grey") +
  geom_text(aes(
    x = 1.95,
    y = -0.033,
    label = paste0("***")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(
    x = 0.95,
    y = -0.033,
    label = paste0("**")
  ),
  size = 10,
  color = cbPalette[1]) +
  geom_text(aes(
    x = 3.05,
    y = -0.033,
    label = paste0("*")
  ),
  size = 10,
  color = cbPalette[8])

# ggsave(
#     "behavioral_slope_across_group.png",
#      width = 15, height = 15, units = "cm"
#  )
```

## Preprocess: calculate within subject standard error for composite scores
```{r}
composite_within_stat <-
  summarySEwithin(
    compositeGroupL,
    measurevar = "composite_score",
    betweenvars = "group",
    withinvars = "task",
    idvar = "part_id",
    na.rm = T,
    conf.interval = .95
  )
colnames(composite_within_stat)[colnames(composite_within_stat) == "group"] <-
  "Group"
composite_within_stat$task <-
  revalue(
    composite_within_stat$task,
    c(
      "composite_lsl" = "Letter",
      "composite_tsl" = "Tone",
      "composite_ssl" = "Syllable",
      "composite_vsl" = "Image"
    )
  )
composite_within_stat$task <-
  factor(composite_within_stat$task,
         levels = c("Letter",
                    "Syllable",
                    "Image",
                    "Tone"))
composite_within_stat$Group <-
  factor(composite_within_stat$Group, levels = c("TD", "ASD"))
```

## Plot Composite Score Line Plot
```{r}
composite_within_stat %>%
  ggplot(aes(x = task, y = composite_score, group = Group)) +
  geom_line(aes(linetype = Group, color = Group),
            position = pd,
            size = 1.8) +
  geom_errorbar(
    aes(ymin = composite_score - se, ymax = composite_score + se),
    width = .1,
    position = pd
  ) +
  geom_point(
    aes(color = Group),
    size = 4,
    position = pd,
    show.legend = FALSE
  ) +
  geom_point(size = 3,
             color = "white",
             position = pd) +
  labs(title = "SL Composite Scores",
       x = "SL Task",  # Change x-axis label
       y = "Composite Score") +
  scale_color_manual(values = c(cbPalette[1], cbPalette[8])) +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme(
    plot.title = element_text(size = 26, face = "bold"),
    axis.title.x = element_text(size = 21, face = "bold"),
    axis.title.y = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 16, face = "bold")
  ) +
  theme(
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold")
  ) +
  theme(
    panel.background = element_rect(fill = "white"),
    # Set plot background to white
    legend.key  = element_rect(fill = "white"),
    # Set legend item backgrounds to white
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1)   # Add line to y axis
  )

# ggsave(
#   "behavioral_composite_across_group.png",
#   bg = "transparent",
#   width = 15,
#   height = 15,
#   units = "cm"
# )
```

## Preprocess: calculate within subject standard error for composite scores in each age group
```{r}
compositeYoungPlot <- summarySEwithin(compositeYoungL, measurevar = "composite_score", betweenvars = "group", 
                                    withinvars = "domain", idvar="part_id", na.rm=T, conf.interval=.95)

compositeYoungPlot$Age <- "Younger"

compositeOldPlot <- summarySEwithin(compositeOldL, measurevar = "composite_score", betweenvars = "group", 
                                    withinvars = "domain", idvar="part_id", na.rm=T, conf.interval=.95)

compositeOldPlot$Age <- "Older"

compositeAgePlot <- rbind(compositeYoungPlot, compositeOldPlot)

compositeAgePlot$domain <- 
  factor(compositeAgePlot$domain,levels = c("composite_ling", 
                                              "composite_nonling"))

colnames(compositeAgePlot)[colnames(compositeAgePlot) == "group"] <- "Group"
compositeAgePlot[which(compositeAgePlot$domain == "composite_nonling"), "Domain"] <- "Nonlinguistic"
compositeAgePlot[which(compositeAgePlot$domain == "composite_ling"), "Domain"] <- "Linguistic"

compositeAgePlot$Domain <- as.factor(compositeAgePlot$Domain)

compositeAgePlot$Age <- 
  factor(compositeAgePlot$Age,
         levels = c("Younger", 
                    "Older"))
compositeAgePlot <- compositeAgePlot[order(compositeAgePlot$Age), ]
```

## Plot Composite Score in Each Age Group
```{r}
library(ggplot2)
library(ggpattern)

labs <- c("Younger Children", "Older Children")
names(labs) <- c("Younger", "Older")

compositeAgePlot %>%
  ggplot(
    aes(
      x = Domain,
      y = composite_score,
      ymin = composite_score - se,
      ymax = composite_score + se,
      group = Group
    )
  ) +
  scale_fill_manual(values = c(cbPalette[1], cbPalette[8])) +
  geom_bar(stat = "identity",
           position = position_dodge(),
           width = 0.9) +
  facet_wrap("Age", labeller = (labeller(Age = labs))) +
  geom_col_pattern(
    aes(
      x = Domain,
      y = composite_score,
      pattern = Domain,
      fill = Group
    ),
    # color = Group
    # pattern = 'stripe',
    position = position_dodge(),
    pattern_density = 0.1,
    pattern_spacing = 0.025,
    pattern_key_scale_factor = 0.6,
    color = "#000000",
    pattern_colour = "black",
    pattern_fill = "black"
  ) +
  scale_pattern_manual(values = c(Linguistic = "stripe", Nonlinguistic = "none")) +
  # scale_fill_grey(start = 0.6, end = 1)+
  guides(pattern = guide_legend(override.aes = list(fill = "white")),
         fill = guide_legend(override.aes = list(pattern = "none"))) +
  geom_errorbar(width = .1, position = position_dodge(width = 0.9)) +
  labs(title = "SL Composite Scores in Younger and Older Children",
       x = "Group",  # Change x-axis label
       y = "SL Composite Score") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    plot.title = element_text(size = 30, face = "bold"),
    axis.title.x = element_text(size = 26, face = "bold"),
    axis.title.y = element_text(size = 22, face = "bold"),
    axis.text = element_text(size = 24, face = "bold"),
    legend.text = element_text(size = 22, face = "bold"),
    legend.title = element_text(size = 22, face = "bold"),
    legend.key = element_rect(color = "black"),
    panel.background = element_rect(fill = "white"),
    # Set plot background to whit
    axis.line.x = element_line(colour = "black", size = 1),
    # Add line to x axis
    axis.line.y = element_line(colour = "black", size = 1),
    # Add line to y axis
    strip.text = element_text(size = 24, face = "bold"),
    # Change facet text
    strip.background = element_rect(fill = "white", size = 1),
    # Change facet color
    panel.spacing = unit(.05, "lines"),
    # Add panel border
    panel.border = element_rect(color = "black", fill = NA, size = 0.5),
    # Change panel border color and size
    legend.position = c(0.06, 0.88),
    legend.background = element_rect(fill = "#ffffff00")
    # strip.text = element_blank()
  ) +
  guides(pattern = FALSE) +
  # geom_text(
  #   size = 14,
  #   color = "black",
  #   data = data.frame(
  #     Group = 0,
  #     composite_score = 0.55,
  #     Age = "Older",
  #     se = 0,
  #     Domain = 0
  #   ),
  #   aes(x = 1.5, y = 0.53, label = paste0("*"))
  # ) +
    geom_text( 
    size = 10,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1.5, y = 0.68, label = paste0("†"))
  ) +
  geom_segment(
    aes(
      x = 1,
      xend = 2,
      y = 0.58,
      yend = 0.58
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) +
  # geom_text(
  #   size = 14,
  #   color = "black",
  #   data = data.frame(
  #     Group = 0,
  #     composite_score = 0.55,
  #     Age = "Older",
  #     se = 0,
  #     Domain = 0
  #   ),
  #   aes(x = 1, y = 0.42, label = paste0("*"))
  # ) +
  geom_text(
    size = 14,
    color = "black",
    data = data.frame(
      Group = 0,
      composite_score = 0.6,
      Age = "Older",
      se = 0,
      Domain = 0
    ),
    aes(x = 1, y = 0.45, label = paste0("**"))
  ) +
  geom_segment(
    aes(
      x = 0.8,
      xend = 1.2,
      y = 0.46,
      yend = 0.46
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) + 
  geom_segment(
    aes(
      x = 1.8,
      xend = 2.2,
      y = 0.46,
      yend = 0.46
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) + 
  geom_segment(
    aes(
      x = 1,
      xend = 1,
      y = 0.53,
      yend = 0.58
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) +
  geom_segment(
    aes(
      x = 2,
      xend = 2,
      y = 0.53,
      yend = 0.58
    ),
    data = data.frame(
      Group = 0,
      composite_score = 0.55,
      Age = "Older",
      se = 0,
      Domain = 0
    )
  ) 
# ggsave("composite_age_median.png",
#         bg="transparent",width = 30, height = 15, units = "cm")
```

# Section 7: Individual difference: Correlations between tasks, age, language

## Caculate correlations between all measures
```{r}
# Correlation matrix between ASD Lingusitic rt slope, composite and SCQ, RBS-R, Age
library("RcmdrMisc")

compositeCorr <- function(df, group) {
  rcorr.adjust(as.matrix(df[which(df$group == group), c(
    "age_at_web_year",
    "a_prime",
    "rbs_r",
    "scq_web",
    "lsl_slope",
    "ssl_slope",
    "vsl_slope",
    "tsl_slope",
    "lsl_acc",
    "ssl_acc",
    "vsl_acc",
    "tsl_acc",
    "composite_lsl",
    "composite_ssl",
    "composite_vsl",
    "composite_tsl",
    "composite_ling",
    "composite_nonling"
  )]),
  use = c("pairwise.complete.obs"))
}

# Extract correlation matrix:
td_corr_posthoc <- compositeCorr(compositeAge, "TD")
write.csv(as.data.frame(td_corr_posthoc$R[1]), "compositeCorrTD.csv")
write.csv(as.data.frame(td_corr_posthoc$R[3]), "compositeCorrPTD.csv")

asd_corr_posthoc <- compositeCorr(compositeAge, "ASD")
write.csv(as.data.frame(asd_corr_posthoc$R[1]), "compositeCorrASD.csv")
write.csv(as.data.frame(asd_corr_posthoc$R[3]), "compositeCorrPASD.csv")

asdOLD_corr_posthoc <- compositeCorr(compositeAgeASDO, "ASD")
tdOLD_corr_posthoc <-  compositeCorr(compositeAgeTDO, "TD")
asdYOUNG_corr_posthoc <- compositeCorr(compositeAgeASDY, "ASD")
tdYOUNG_corr_posthoc <-  compositeCorr(compositeAgeTDY, "TD")

# Flatten correlation matrix for plotting:
flattenCorrMatrix <- function(cormat, pmat, nmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  = (cormat)[ut],
    p = pmat[ut],
    n = nmat[ut]
  )
}

# Correlations wihtin all TD
td_corr_posthoc <-
  flattenCorrMatrix(data.frame(td_corr_posthoc$R[1]),
                  data.frame(td_corr_posthoc$R[3]),
                  data.frame(td_corr_posthoc$R[2]))
# Correlations wihtin all ASD
asd_corr_posthoc <-
  flattenCorrMatrix(data.frame(asd_corr_posthoc$R[1]),
                  data.frame(asd_corr_posthoc$R[3]),
                  data.frame(asd_corr_posthoc$R[2]))
# Correlations wihtin older TD
tdOLD_corr_posthoc <-
  flattenCorrMatrix(data.frame(tdOLD_corr_posthoc$R[1]),
                  data.frame(tdOLD_corr_posthoc$R[3]),
                  data.frame(tdOLD_corr_posthoc$R[2]))
# Correlations wihtin older ASD
asdOLD_corr_posthoc <-
  flattenCorrMatrix(data.frame(asdOLD_corr_posthoc$R[1]),
                  data.frame(asdOLD_corr_posthoc$R[3]),
                  data.frame(asdOLD_corr_posthoc$R[2]))
# Correlations wihtin younger TD
tdYOUNG_corr_posthoc <-
  flattenCorrMatrix(data.frame(tdYOUNG_corr_posthoc$R[1]),
                  data.frame(tdYOUNG_corr_posthoc$R[3]),
                  data.frame(tdYOUNG_corr_posthoc$R[2]))
# Correlations wihtin younger ASD
asdYOUNG_corr_posthoc <-
  flattenCorrMatrix(data.frame(asdYOUNG_corr_posthoc$R[1]),
                  data.frame(asdYOUNG_corr_posthoc$R[3]),
                  data.frame(asdYOUNG_corr_posthoc$R[2]))
```

### 2021-07-22 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd

@@
   group_by(group, task) %>%
+  filter(!is.na(reaction_time)) %>%
   summarize(n = length(unique(id))) %>%

### 2021-07-22 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd

@@
 
-## RT Model that has isSingular Warning:
-```{r}
-# isSingular Warning:
+## RT Model:
+```{r}
 lmer_slope_m1 <-
@@
 ```{r}
-# Using raw reaction time and controlling for mean reaction time (isSingular Warning; Scaling issues)
+# Using raw reaction time and controlling for mean reaction time (Scaling issues)
 lmer_slope_m2 <-
@@
 ```
-## SL Cross-sectional Development Analyses: Younger group model has isSingular Warnings
+## SL Cross-sectional Development Analyses:
 ```{r}
@@
 
-# Younger group has isSingular Warnings
+# Younger group
 age_composite_m3 <- 

### 2021-08-08 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd
Updated outlier removal for by trial RT data frame. Outliers were already removed from the data file read into the script. The function to remove outliers from the by trial RT data was not necessary.

@@
 ```{r, include = F}
+# Outliers already removed in the data file (just to double check the removal)
 rt_trial <- read.csv("rt_trial.csv")
@@
     if (length(part_id) != 0) {
-      rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
+    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
     }
@@
   filter(!is.na(reaction_time)) %>%
-  summarize(n = length(unique(id))) %>%
+  dplyr::summarise(n = length(unique(id))) %>%
   slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
@@
 
-## SL Cross-sectional Development Analyses: Post-hoc t-test of Linguistic SL Composite Scores in each age group
-```{r}
-# Younger group:
-t.test(compositeAgeTDY$composite_ling, compositeAgeASDY$composite_ling, alternative = "greater")
-# Older group:
-t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling, alternative = "greater")
+## SL Cross-sectional Development Analyses: Post-hoc t-test of Linguistic and Nonlinguistic SL Composite Scores in older children
+```{r}
+# Older group linguistic:
+t.test(compositeAgeTDO$composite_ling, compositeAgeASDO$composite_ling)
+# Older group nonlinguistic
+t.test(compositeAgeTDO$composite_nonling, compositeAgeASDO$composite_nonling)
 ```

### 2021-08-08 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd
Updated outlier removal function for by trial RT data again. Outliers were already removed from the data. The function is not necessary but still kept in the script to double check outliers.

@@
 
-    if (length(part_id) != 0) {
+    if (length(which(rt_trial$id %in% part_id & rt_trial$task == taskName)) != 0) {
     rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]

### 2021-08-08 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd
Changed variable names in the by-trial RT outlier removal function. This function is not necessary. Outliers were already removed in the data.

--- 2021-08-08 script/manuscript_clean_061021.Rmd
@@
 outlier_extract_trial_rt <-
-  function(DF, task) {
-    part_id <- DF[which(DF$task == task), "part_id"]
-
-    if (length(part_id) != 0) {
-    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
+  function(DF, taskName) {
+    part_id <- DF[which(DF$task == taskName), "part_id"]
+
+    if (length(which(rt_trial$id %in% part_id & rt_trial$task == taskName)) != 0) {
+    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == taskName), ]
     }
